\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{tgtermes}
\fontfamily{Georgia}
\usepackage{fontawesome5}
\usepackage{xcolor}
\definecolor{link_color}{HTML}{9F8170}
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=link_color!70!black
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge {\color{Mahogany}{Farzan Dehbashi}}} \vspace{1mm} \\ \textbf{ \color{Mahogany} Software Engineer} &Email : \href{mailto:farzan.dehbashi95@gmail.com}{farzan.dehbashi95@gmail.com}\\ 
  
   \href{ https://github.com/farzan-dehbashi}{\faGithub \, Github} | \href{https://scholar.google.com/citations?hl=en&user=iWgKz8YAAAAJ}{ \faGraduationCap \, Google Scholar} |  \href{https://www.linkedin.com/in/farzandb}{\faLinkedin \, Linkedin} & \faIcon[solid]{phone-square-alt} +1-519-589-1234  \\
\end{tabular*}


%-----------EDUCATION-----------------
\vspace{-3mm}
\section{\color{Mahogany}Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Master of Computer Science;  GPA: 3.9/4.0}{Sep. 2018 -- Sep. 2020}

      
    \resumeSubheading
      {Amirkabir University of Technology}{Tehran, Iran} 
      {Bachelor of Computer Engineering;  GPA: 3.4/4.0}{Sep. 2013 -- Sep. 2018} \\ \vspace{2mm} \scriptsize{Courses: Algorithms, Data Structure, Software engineering, Advanced Programming, Web Development, Operating Systems}
      
  \resumeSubHeadingListEnd
  
 \vspace{-8mm} 
%-----------EXPERIENCE-----------------
\section{\color{Mahogany}Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Waterloo{\normalfont , Department of Computer Science}}{Waterloo, ON}
      {Research Assistant I}{Sep 2020 - Dec 2021}
      \resumeItemListStart
        \resumeItem{}
          {Design and implementation of an RFID reader software to automate data collection, visualization, and analysis using Python (Pandas, Sllurp, Matplotlib, Seaborn) and Bash}
         \resumeItem{}
          {Worked closely with 3 professors from UCLA and University of Waterloo for designing and prototyping of a new touch sensing device using RFID with 9$\times$ lower cost and 2.4$\times$ range improvement. Capable of detecting user gesture by 98.6 \% accuracy. Collected, visualized and analyzed a dataset of 700K+ samples using Python.}
      \resumeItemListEnd
      
      \resumeSubheading
      {University of Waterloo{\normalfont , Department of Computer Science}}{Waterloo, ON}
      {Graduate Research Assistant}{Sep 2018 - Sep 2020}
      \resumeItemListStart
        \resumeItem{}
          {Prototyping and implementation of an IoT Embedded system with 3$\times$ less power consumption and battery-life, 60\% lower cost per unit and simpler design; using Python, C running on Google Home WiFi routers. Also, securing a US Patent based on this design. For more details, refer to my WiTAG paper.}
          \resumeItem{}
          {Prototyping and implementation and testing of a drowning detection software, which leverages RFID signal. Using Python (Pandas, Sllurp, Numpy, Matplotlib)
          }
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
 \vspace{-8mm}
%--------PROGRAMMING SKILLS------------
\section{\color{Mahogany}Technical Skills}
%  \resumeSubHeadingListStart
%   \item{
     {\textbf{Python} (Numpy, Pandas, Matplotlib, Seaborn, Pytorch(familiar), OpenCV(familiar), Pygame), \textbf{C++}, Docker, \textbf{SQL}(MySQL), \textbf{Bash}, Git, HTML/CSS, C(familiar), Java(familiar), Unix/Linux environment}
%   }
%   \item{Exposure: C, Java, }
%  \resumeSubHeadingListEnd
 
\vspace{-4mm}
%-----------PROJECTS-----------------
\section{\color{Mahogany}Open-source Projects}
  \resumeSubHeadingListStart
    % \item{Tetris game}
    %   {React}
     \item{\textbf{ \href{https://github.com/farzan-dehbashi/Whatsapp}{ Whatsapp  \faGithub \, :}}} 
     Design and implementation of a messenger app that enables multiple users to send messages, images, files and follow each other; implemented the server, client, and network connection using Python based on object-oriented design. 
     \vspace{-2mm}
     \item{\href{https://github.com/farzan-dehbashi/telegram_bot}{\textbf{Telegram Bot \faGithub \, :}}}
     Implementation of a Telegram Bot by python using \textbf{TensorFlow, OpenCV, Telegram API and Numpy} library, to classify user images.
     \vspace{-2mm}
     \item{\href{https://github.com/farzan-dehbashi/snake_game}{\textbf{Snake game \faGithub \, :}}}
     Implementation of a Nokia Snake Game by python using \textbf{Pygame} library, which is shipped using either a \textbf{Docker} container or an executable file.
     \vspace{-2mm}
    \item{\href{https://github.com/farzan-dehbashi/WiFi-Backscattery-simulator/blob/master/README.md}{\textbf{ WiFi packet simulator \faGithub \, :}} A multi-modal WiFi backscatter packet simulator to assess probability of successful transmission in noisy environment using Python; capable of estimation by 96\%+ accuracy.}
     
    
    % \resumeSubItem{Github Visualization}
    %   {Data Visualization of Git Log data using D3 to analyze project trends over time.}
   
  \resumeSubHeadingListEnd

 


\vspace{-8mm}
%-------------------------------------------
\section{\color{Mahogany}Publications}
 \resumeSubHeadingListStart
 \item{\href{https://patentimages.storage.googleapis.com/a2/38/c3/7013ac293ff7c3/US20210288755A1.pdf}{\textbf{US Patent:} Channel disruption wireless communication system}}
 \vspace{-2mm}
 \item{\href{https://cs.uwaterloo.ca/~brecht/papers/wifi-vs-rfid-mobicom-2021.pdf}{\textbf{Verification: Can WiFi Backscatter Replace RFID?}}  \small{ACM MobiCom 2021 (Acceptance rate: 17\%)}
 \vspace{-2mm}
 \item{
    \href{http://web.cs.ucla.edu/~omid/Papers/Sigcomm20.pdf}{
        \textbf{WiTAG: Seamless WiFi Backscater Communication}}\small{, ACM SIGCOMM 2020 (Acceptance rate: 21\%)}
    }
 \vspace{-2mm}  
 \item{
    \href{https://www.researchgate.net/profile/Farzan-Dehbashi/publication/335186643_SwimTrack_Drowning_Detection_using_RFID/links/5ee0fa8f299bf13a8910118f/SwimTrack-Drowning-Detection-using-RFID.pdf}{
        \textbf{SwimTrack: Drowning Detection using RFID}} \small{, ACM SIGCOMM 2019 (Acceptance rate:  14\%)}
    }
 }
  \resumeSubHeadingListEnd
 
\vspace{-8mm}
 %-------------------------------------------
\section{\color{Mahogany}Certificates}
\href{https://github.com/farzan-dehbashi/web_page/blob/main/certificates/python.pdf}{Python Programming Masterclass \footnotesize{(Udemy)}},
     \href{https://github.com/farzan-dehbashi/web_page/blob/main/certificates/SQL.pdf}{MySQL Bootcamp \footnotesize{(Udemy) }},
     
     \href{https://github.com/farzan-dehbashi/web_page/blob/main/certificates/bash.pdf}{Complete Linux Bash Shell Scripting\footnotesize{( Udemy)} },
     \href{https://github.com/farzan-dehbashi/web_page/blob/main/certificates/docker.pdf}{Docker Mastery \footnotesize{(Udemy)}
     }



 %-------------------------------------------
% \section{\color{Mahogany}Hobbies}
% Photography, camping, travel
\end{document}
